When are Fuzzy Extractors Possible?

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
modifications to techniques discussion and removal of Interpreting Our Results

On the other hand, there is a family of sources, $\mathcal{W}_Z$, where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\paragraph{Interpreting our Results}
Our results show that fuzzy min-entropy is sufficient for noisy key derivation if the distribution is precisely known but insufficient if the distribution is only known to come from a family.  A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.  Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.  This impossibility can be overcome by the use of a short seed of uniform randomness.  
We must find an analogous relaxation to derive keys from noisy sources.  One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.

@@

\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).   Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

@@

\paragraph{Techniques for Negative Results for Distributional Uncertainty}
We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$.
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
the adversary knows $W_z$.   To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.

>>>>

On the other hand, there is a family of sources, $\mathcal{W}_Z$,
where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for
which no secure sketch correcting even a few errors is
possible~(\thref{thm:imposs sketch}). The impossibility result applies
even when $\rec$ is allowed to be incorrect with probability up to
$1/4$ (in contrast to our fuzzy extractor impossibility result, which
requires perfect reconstruction).

% \paragraph{Interpreting our Results}
% Our results show that fuzzy min-entropy is necessary and sufficient for noisy key
% derivation if the distribution is precisely known. We give evidence
% that fuzzy min-entropy alone is not sufficient when the exact
% distribution is uncertain.  
%  % but insufficient if the distribution is only known to come from a
%  % family. 
%  A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.  Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.  This impossibility can be overcome by the use of a short seed of uniform randomness.  
% We must find an analogous relaxation to derive keys from noisy sources.  One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.

@@

\paragraph{Techniques for Positive Results for a Precisely Known
  Distribution} 
We now explain how to construct a secure sketch for a precisely known
distribution $W$ with fuzzy min-entropy (we already explained how to
construct a fuzzy extractor from it).  We begin with distributions in
which all points in the support have the same probability (so-called
``flat'' distributions).  Consider some subsequent reading $w'$. To
achieve correctness, the sketch algorithm must disambiguate which
point $w\in W$ within distance $t$ of $w'$ was
sketched. Disambiguating multiple points can be accomplished by
universal hashing, as long as the size of hash output space is
slightly greater than the number of possible points. Thus, our sketch
is computed via a universal hash of $w$. To determine the length of
that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
$t$. Because the distribution is flat, $B^*$ is also the ball with the
most points of nonzero probability. Thus, the length of the sketch
needs to be slightly greater than the logarithm of the number of
non-zero probability point in $B^*$. Since $\Hfuzz(W)$ is
determined by the weight of that ball, the number of points cannot be
too high and there will be entropy left after the sketch is published.
%
This remaining entropy is sufficient for extracting a key.

@@

\paragraph{Techniques for Negative Results for Distributional Uncertainty}
We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$.
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
the adversary knows $W_z$.   To exploit the asymmetry, we construct
$\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the
outcome $z$) reduces the distribution to a single affine line, but
conditioning on \emph{only} $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.
